Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-01-30 Draft/scanNLO.tex
commented some plots in scanNLO.tex

\begin{figure}[hbt]
\centering
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/ptj3_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj2_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zmu_nlo.pdf}}
\caption{{\bf FIGURES STILL TO BE MODIFIED} } \label{fig:mjjdyjj_1d_3}
\end{figure}

>>>>

%\begin{figure}[hbt]
%\centering
%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/ptj3_nlo.pdf}}
%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj2_nlo.pdf}}
%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
%\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zmu_nlo.pdf}}
%\caption{{\bf FIGURES STILL TO BE MODIFIED} } \label{fig:mjjdyjj_1d_3}
%\end{figure}
